
\noindent \textbf{Question 1}: Write the static admissibility equations! \\

\textbf{Answer:} Find $\sigmauu $ symmetric such that 
\begin{equation}
\begin{split}
& \text{(a)  } \sigmauu \cdot \underline{n} = \underline{0} \quad \forall \text{ } M \in S_e \quad \text{Boundary equation} \\
& \text{(b)  } \sigmauu \cdot \underline{n} = - p_0 \underline{n} \quad \forall \text{ } M \in S_i \quad \text{Boundary equation} \\
& \text{(c)  } \divu \sigmauu = \underline{0} \quad \forall \text{ } M \in \Omega \quad \text{Internal equilibrium}
\end{split}
\end{equation}

\noindent \textbf{Question 2}: Please expand this equation using spherical  coordinates system! \\

\textbf{Answer:} In spherical coordinates,
\begin{equation}
\sigmauu = \left[
\begin{matrix}
\sigmarr & \sigmart & \sigmarf \\
\sigmart & \sigmatt & \sigmatf \\
\sigmarf & \sigmatf & \sigmaff 
\end{matrix}
\right]
\end{equation}

From Eq. (a),
\begin{equation}
\sigmarr(r = R_e,\theta,\varphi) = \sigmart (r=R_e,\theta,\varphi) = \sigmarf(r=R_e,\theta,\varphi) = 0
\end{equation}

From Eq. (b),
\begin{equation}
\begin{split}
& -\sigmarr(r=R_i,\theta,\varphi) = p_0 \\
& -\sigmart(r=R_i,\theta,\varphi) = 0 \\
& -\sigmarf(r=R_i,\theta,\varphi) = 0
\end{split}
\end{equation}

From Eq. (c) $\rightarrow$ See Textbook equation 1.11a (divergence with spherical coordinates)



\noindent \textbf{Question 3}: Let's assume that the following stress tensor 
\begin{equation}
\sigmauu = \left[ \begin{matrix}
\sigmarr &0 &0 \\
0 & \sigmatt & 0 \\
0 & 0 & \sigmaff
\end{matrix} \right]
\end{equation}
with 
\begin{equation}
\sigmarr = -A\left[\frac{B}{r^3} - 1 \right]
\end{equation}
and 
\begin{equation}
\sigmatt = \sigmaff = A \left[\frac{B}{2r^3} + 1 \right]
\end{equation}
Please calculate the coefficient $A$ and $B$ so that $\sigmauu$ could be a solution of the problem! \\ 

\textbf{Answer:} Using the proposed stress tensor, and expanding equation (c), we get
\begin{equation}
\begin{split}
& \derp{\sigmarr}{r} + \frac{2\sigmarr - \sigmatt - \sigmaff}{r} = 0 \\
& 0 = 0 \\
& 0 = 0
\end{split}
\end{equation}
We now check if $\sigmauu$ ca fulfill the static admissibility equations.
\begin{equation}
\derp{\sigmarr}{r} + \frac{2\sigmarr - \sigmatt - \sigmaff}{r} = \frac{3AB}{r^4} - \frac{3AB}{r^4} = 0 \rightarrow \text{(c) is OK. Interior equilibrium is satisfied.}
\end{equation}
\begin{equation}
\text{(a)} \rightarrow - A\left[
\frac{B}{R_e^3} - 1 \right] = 0 \rightarrow B = R_e^3
\end{equation}

\begin{equation}
\text{(b)} \rightarrow - A\left[
\frac{R_i^3}{R_e^3} - 1 \right] = p_0 \rightarrow A = p_0 \frac{R_e^3}{R_i^3 - R_e^3}
\end{equation}\\

All the other conditions concerning $\sigmatr$ and $\sigmarf$ are automatically satisfied due to the chosen stress tensor. Thus, a statically admissible stress field is:
\begin{equation}
\sigmauu = \left[
\begin{matrix}
p_0 \frac{R_e^3}{R_i^3 - R_e^3} \left[
\frac{R_i^3}{r} - 1 \right] & 0 & 0 \\
0 & -p_0 \frac{R_e^3}{R_e^3 - R_i^3} \left[
\frac{R_e^3}{2r^3} + 1 \right] & 0 \\
0 & 0 & -p_0 \frac{R_e^3}{R_e^3 - R_i^3} \left[
\frac{R_e^3}{2r^3} + 1 \right]
\end{matrix}
\right]
\end{equation} \\



\noindent \textbf{Question 4}: Please calculate the strain tensor $\epsuu$? Does it satisfy the compatibility equation? Conclusion?

\textbf{Answer:} Based on the constitutive equation, we can calculate the strains:
\begin{equation}
\epsuu = \frac{1+\nu}{E} \sigmauu - \frac{\nu}{E} \text{tr} \sigmauu \underline{\underline{1}}
\end{equation}
\begin{equation}
\text{tr}\sigmauu = -p_0 \frac{R_e^3}{R_e^3 - R_i^3}
\end{equation}
Thus, we get $\epsrt = \epstf = \epsft = 0$. Let us note that 
\begin{equation}
A_1 = p_0 \frac{R_e^3}{R_e^3 - R_i^3}
\end{equation}

We get:
\begin{equation}
\epsuu =  \left[
\begin{matrix}
\left(\frac{1+\nu}{E}\right) A_1 \left[
\frac{R_e^3}{r} - 1 \right] + \frac{\nu}{E} A_1 & 0 & 0 \\
0 & -\left(\frac{1+\nu}{E}\right) A_1 \left[
\frac{R_e^3}{2r^3} + 1 \right] + \frac{\nu}{E} A_1 & 0 \\
0 & 0 & -\left(\frac{1+\nu}{E}\right) A_1 \left[
\frac{R_e^3}{2r^3} + 1 \right] + \frac{\nu}{E} A_1
\end{matrix}
\right]
\end{equation} \\

In case of complete spherical symmetry, the compatibility equation can be simplified (see Textbook equation 2.14b):
\begin{equation}
\frac{d\epsff}{dr} + \frac{\epsff- \epsrr}{r} = 0
\end{equation}
Let us verify if this equation is satisfied by $\epsuu$.
\begin{equation}
\frac{d\epsff}{dr} = 3A_1 \left(\frac{1+\nu}{E}\right) \frac{R_e^3}{2r^4}
\end{equation}
\begin{equation}
\frac{\epsff - \epsrr}{r} = -3A_1 \left(\frac{1+\nu}{E}\right) \frac{R_e^3}{2r^4}
\end{equation} \\

The two equations above satisfied the compatibility equation. Thus it will be possible to integrate $\epsuu$ to determine a displacement field $\underline{u}$. Considering there is no additional kinematic condition (no kinematic boundary condition), we got the exact solution of the problem.

